A Hexagon Tile Map Algorithm for Displaying Spatial Data

### 2020-10-18 kobakian-cook.tex
simplified images

\begin{Schunk}
\begin{figure}
\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/centroids_plot-1} \caption[The Australian Cancer Atlas data has determined the colour of each Statistical Area of Australian at Level 2]{The Australian Cancer Atlas data has determined the colour of each Statistical Area of Australian at Level 2. A choropleth map (a) of Standardised Incidence Rates (SIRs) is paired with a hexagon tile map (b) to contrast the colours that are made obvious when every SA2 is equally represented.}\label{fig:centroids_plot}
\end{figure}
\end{Schunk}

@@

A set of longitude columns, and latitude rows are created to define the
locations of the hexagons. The distance between each row and column is
the size specified by \texttt{hex\_size}. Equally spaced columns are
created from the minimum longitude minus the buffer distance, up to the
maximum longitude plus the buffer distance. Similarly, the rows are
created from the latitude values and the buffer distance. A unique
hexagon location is created from all intersections of the longitude
columns and latitude rows. Figure \ref{fig:grid2} shows the original
grid on the left, to allow for tessellating hexagons, every second
latitude row on the grid is shifted right, by half of the hexagon size.
The grid for tessellation is shown on the right.

\begin{Schunk}
\begin{figure}
\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/grid2-1} \caption[Complete set of grid points to create a tile map]{Complete set of grid points to create a tile map.}\label{fig:grid2}
\end{figure}
\end{Schunk}

@@

\begin{Schunk}
\begin{figure}
\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/grid3-1} \caption[The remaining hexagon locations from all the possible points in the initial grid after the buffer is applied]{The remaining hexagon locations from all the possible points in the initial grid after the buffer is applied. The blue dots show the grid points left to choose from after the buffer step.}\label{fig:grid3}
\end{figure}
\end{Schunk}

@@

\begin{Schunk}
\begin{figure}
\includegraphics[width=1\linewidth]{kobakian-cook_files/figure-latex/buffers-1} \caption[Filter for grid points within a square, then circular, distance for those closest to the centroid]{Filter for grid points within a square, then circular, distance for those closest to the centroid.}\label{fig:buffers}
\end{figure}
\end{Schunk}

The \texttt{width} parameter is used to take a slice of the remaining
points. The width is the amount of degrees used on either side of the
angle from the focal point to centroid location. This uses the angle
from the closest capital city, to the current centroid as seen in Figure
\ref{fig:buffers2} . This allows the spatial relationship to be
preserved, even when it is allocated to a hexagon that is further from
the focal point then the original centroid location.

\begin{Schunk}
\begin{figure}
\includegraphics[width=1\linewidth]{kobakian-cook_files/figure-latex/buffers2-1} \caption[Filter for grid points within a square, then circular, distance for those closest to the centroid]{Filter for grid points within a square, then circular, distance for those closest to the centroid.}\label{fig:buffers2}
\end{figure}
\end{Schunk}

@@

A complete hexagon tile map of Tasmania is created by applying the
algorithm steps to each centroid. The hexagon tile map is used to
visualise the Australian Cancer Atlas data \citep{TACA}. Two views of
the same data are produced by filling according to the thyroid Cancer
Standardised Incidence Rates (SIRs) downloaded from the Australian
Cancer Atlas site. This small example in Figure \ref{fig:centroids_plot}
shows the group of blue areas in the Hobart CBD more prominently in the
hexagon tile map (b). The small red areas visible in the choropleth map
(a) along the north coast are much larger in the hexagon tile maps. The
hexagon tile map shows less yellow, this no longer overwhelms the map
space with the information regarding the rural areas.

>>>>

@@

A set of longitude columns, and latitude rows are created to define the
locations of the hexagons. The distance between each row and column is
the size specified by \texttt{hex\_size}. Equally spaced columns are
created from the minimum longitude minus the buffer distance, up to the
maximum longitude plus the buffer distance. Similarly, the rows are
created from the latitude values and the buffer distance. A unique
hexagon location is created from all intersections of the longitude
columns and latitude rows. Figure \ref{fig:filterprocess} shows the
original grid on the left, to allow for tessellating hexagons, every
second latitude row on the grid is shifted right, by half of the hexagon
size. The grid for tessellation is shown on the right.

@@

@@

The \texttt{width} parameter is used to take a slice of the remaining
points. The width is the amount of degrees used on either side of the
angle from the focal point to centroid location. This uses the angle
from the closest capital city, to the current centroid as seen in Figure
\ref{fig:filterprocess} . This allows the spatial relationship to be
preserved, even when it is allocated to a hexagon that is further from
the focal point then the original centroid location.

\begin{Schunk}
\begin{figure}
\includegraphics[width=1.2\linewidth]{kobakian-cook_files/figure-latex/filterprocess-1} \caption[Filter for grid points within a square, then circular, distance for those closest to the centroid]{Filter for grid points within a square, then circular, distance for those closest to the centroid.}\label{fig:filterprocess}
\end{figure}
\end{Schunk}

@@

A complete hexagon tile map of Tasmania is created by applying the
algorithm steps to each centroid. The hexagon tile map is used to
visualise the Australian Cancer Atlas data \citep{TACA}. Two views of
the same data are produced by filling according to the thyroid Cancer
Standardised Incidence Rates (SIRs) downloaded from the Australian
Cancer Atlas site. This small example in Figure \ref{fig:filterprocess}
shows the group of blue areas in the Hobart CBD more prominently in the
hexagon tile map (b). The small red areas visible in the choropleth map
(a) along the north coast are much larger in the hexagon tile maps. The
hexagon tile map shows less yellow, this no longer overwhelms the map
space with the information regarding the rural areas.
